---
title: "Test Model Run"
output: html_notebook
---

# Step 1: Read in required libraries

```{r}
library(dynatopmodel)
library(sp)
library(raster)
library(reticulate)
library(topmodel)
library(ggplot2)
library(mapview)
library(hydroPSO)                                               # Read in hydroPSO algorithm
library(hydroGOF)                                               # Read in hydroGOF package (goodness of fit)
library(hydroTSM)                                               # Read in hydroTSM package
library(boot)                                                   # Read in boot package
library(zoo)                                                    # Read in zoo package for time series analysis 
library(sensitivity)                                            # Read in the sensitivity analysis package
library(xts)                                                    # Read in the xts package also for time series 
library(ggplot2)                                                # Read in ggplot2 package for figure 
library(dplyr)                                                  # Read in dplyr package
library(readr)                                                  # Read in read r package
library(lubridate)                                              # Read in lubridate for date manipulation
library(Evapotranspiration)                                     # Read in the Evapotranspiration packahge 
library(rasterVis)                                              # Read in the rasterVis package for raster 
library(dismo)                                                  # Read in dismo package for k fold cross
library(rgl)                                                    # Read in the rgl package for 3D scatter plots
library(matrixStats)                                            # Read in the library for matrixStats
library(gridExtra)                                              # Read in the gridExtra package for GGPLOT2
library(tidyquant)

```

# Step 2: Load in Spatial Data 
Note, this should be saved from the 'run-modular-discretization.Rmd' Notebook 

```{r}
# Read in the data 
read.spatial <- readRDS('SpatialInputData/dynatop_spatial_LM.RData')
disc <- read.spatial$disc                                      
RoutingTable <- read.spatial$RoutingTable                      
explicit.reach.table <- read.spatial$explicit.ChanTable         

# Read the HRUs and assign unique soil groups  
no.hru <- as.numeric(length(unique(disc$hru)))                  
 
soils <- matrix(nrow=no.hru,ncol=1)                                        # Initialize the soils 

for (i in 1:no.hru) {                                           # The loop will output the soil type 
  print(unique(disc$hru)[i])
  soil.type <- unique(disc$layers$soils[disc$hru==unique(disc$hru)[i]])                   # Identifies the soil type for a corresponding HRU
  soils[i] <- soil.type[i]                                                                          
}                                                               # End the loop
disc$groups <- cbind(disc$groups,soils)                   # The soil type is bound to the groups layer

```

# Step 3: Read in the hydrometeorological data 
Note, this should be saved from the 'run-modular-hydro-data.Rmd' Notebook. 
Reminder: if any functions are used to develop the time series that are created within, they must be loaded prior to running the chunk. For initial testing, Forcing.input was loaded from the Calibration_02SEPT21_ExplicitReaches.R document

```{r}
# Specify the Model Time Step (and internal time step)
model.timestep <- 2                                             # Time step of the model (in Hours)
in.timestep <- 1           #2                                     # Specify the number of internal time steps (unitless) - this is for the internal loop to calculate the baseflow

# Specify Calibration Period
calibration.initial <- "2003-11-23 20:00:00"                    # Calibration start       # 
calibration.final <- "2006-09-30 20:00:00"                      # Calibration end         # 

# Specify Warmup Period
warmup.initial <- "2003-05-23 20:00:00"                         # Warmup start            #  
warmup.final <- "2003-11-24 00:00:00"                           # Warmup end              # 

#NOTE: FOR SOME REASON AT THIS TIME STEP THE WINDOW FUNCTION IS ADDING TWO TIME STEPS 

# Concatinate the dates
dates.df <- data.frame(calibration.initial, calibration.final,  # Concatinate the dates into a df 
                       warmup.initial, warmup.final)            # Continued
names.dates <- c('calibration.initial','calibration.final',     # Create names for the df
                 'warmup.initial','warmup.final')               # Continued
names(dates.df) <- names.dates                                  # Specify the date names 

# Specify the watershed area
watershed.area <- sum(disc$groups$area)                                     # Specify the watershed area (m^2) for Falling Rock

# Load in Met and Qobs time series from csv, manipulate to the desired time step, and write the function output to variables
# NOTE: we would also want to put validation initial/final dates.
# If the validation and calibration periods are not one after the other, need a second warm up period. 
input.timeseries <- Forcing.input(dt=model.timestep,            # Run the forcing input function
                                  dates.df=dates.df,            # Start and end dates and watershed area
                                  watershed.area=watershed.area,# Output is a list of three zoo objects for the rain, PET, and Qobs time series
                                  )                             # Input
rain.calib <- input.timeseries$P[1:(length(input.timeseries$P))]                     # Writing the P TS to a variable
PET.calib <- input.timeseries$PET[1:(length(input.timeseries$PET))]                  # Writing the PET TS to a variable
Q.obs.calib <- input.timeseries$Qobs[1:(length(input.timeseries$Qobs))]              # Writing the Qobs TS to a variable
dates.cal.warm <- time(rain.calib)  
```

# Step 4: Set up the parameter values 
```{r}

# Set up the model parameters; Read in min and max values (these values should be based on the literature).
v.of.min <- 10; v.of.max <- 150                                 # Overland flow velocity (m/hr) min and max
m.min <- -9.908; m.max <- -2.813                                # Form of exponential decline in conductivity (m) min and max
srz.max.min <-  .01; srz.max.max <- .75                         # Max root zone storage (m) min and max
srz.0.min <- 0.5; srz.0.max <- 1                                # Initial root zone storage (fraction) min and max
v.chan.min <- 500; v.chan.max <- 7000                           # Channel routing velocity (m/hr) min and max
natlog.T0.min <- 3; natlog.T0.max <- 16                         # Lat saturated transmissivity (m^2/hr) min and max
sd.max.min <- 0.2; sd.max.max <- 0.8                            # Max effective deficit of sat zone (m) min and max
td.min <- 0.01; td.max <- 100                                   # Unsat zone time delay (hr/m) min and max
mann.n.min <- 0.01; mann.n.max <- .15                           # Manning's (unitless) n min and max
S0.min <- 0.01; S0.max <- 0.3                                   # Nominal slope (fraction) min and max
CD.min <-  0.01; CD.max <- 0.5                                  # Capilary drive (unused) min and max
k0.min <-  0.1; k0.max <- 1000                                  # Initial saturated hydraulic conductivity (m/hr; unused) min and max
m1.min <- -9.908; m1.max <- -2.813                              # Assign range for the first m     
m2.min <- -9.908; m2.max <- -2.813                              # Assign range for the second m
m3.min <- -9.908; m3.max <- -2.813                              # Assign range for the third m 

# Concatinate parameter minmum, maximum, and names. Assign names to vectors
lower <- c(v.of.min, m.min, srz.max.min, srz.0.min, v.chan.min, # Vector of lower parametr values
           natlog.T0.min, sd.max.min, td.min,                   # Will be used to generate parameter sets 
           mann.n.min, S0.min, CD.min, k0.min,                  # Continued
           m1.min, m2.min, m3.min)                              # During calibration

upper <- c(v.of.max, m.max, srz.max.max, srz.0.max, v.chan.max, # Vector of upper parameter values
           natlog.T0.max, sd.max.max, td.max,                   # Will be used to generate parmeter sets 
           mann.n.max, S0.max, CD.max, k0.max,                  # Continued 
           m1.max, m2.max, m3.max)                              # During Calibration 

name.params <- c('v.of', 'm','srz.max','srz.0',                 # Create names of all parameters
                 'v.chan','natlog.T0','sd.max',                 # Included in Dynatopmodel
                 'td','mann.n','S0','CD','k0',                  # Continued
                 'm1','m2','m3')                                # To be implemented within the uncertainty and calibration
names(lower) <- name.params                                     # Specify names of columns for the lower part of the parameter space
names(upper) <- name.params                                     # Specify names of columns for the upper part of the parameter space

params <- lower+(upper-lower)/2                                 # Unused - but for a test run of the model

params.best.FC4 <- c(0.978,-6.75, 0.679,0.981,500,5.76,.606,1.58,0.0376,.181,.136,.0693,-9.91,-3.22,-2.81)

```

# Step 5: Run the model with random values and the optimal parameterziation from the previous model

Note: I'm not expecting for the calibration statistics for either model to be particularly good initially since this is a different spatial parameterization... but we'll see. 

```{r}
# Run a test of the model to make sure that things look good before running the PSO calibration 
result.test <- runPSOCalibrationTopmodel(param.values=params,                      # TEST - Run the model with the optimal parameter set
                                         inner.timesteps = in.timestep,            # input the inner.timesteps
                                         rains = rain.calib, PETs=PET.calib,       # All forcing components are the same
                                         obss=Q.obs.calib, discs=disc,          # Spatial information comes from the dynatop spatial function
                                         RoutingTables=NULL,                       # See above
                                         dates.dfs = dates.df)                     # Calibration end date input
result.test.FC4 <- runPSOCalibrationTopmodel(param.values=params.best.FC4,                      # TEST - Run the model with the optimal parameter set
                                             inner.timesteps = in.timestep,            # input the inner.timesteps
                                             rains = rain.calib, PETs=PET.calib,       # All forcing components are the same
                                             obss=Q.obs.calib, discs=disc,          # Spatial information comes from the dynatop spatial function
                                             RoutingTables=NULL,                       # See above
                                             dates.dfs = dates.df)                     # Calibration end date input

```

# Step 6: plot the data 

```{r}
out.sim <- result.test.FC4$run$qsim
obs <- result.test.FC4$run$qobs

out.sim <- out.sim[1:length(obs)]

out <- data.frame('sim'=out.sim,'obs'=obs)

NSE(sim=out$sim,obs=out$x)
NSE(sim=log(out$sim),obs=log(out$x))
KGE(sim=out$sim,obs=out$x)
KGE(sim=log(out$sim),obs=log(out$x))

plot(out$sim,type='l') 
lines(out$x,type='l',col='red')


out.sim.2 <- result.test$run$qsim
obs.2 <- result.test$run$qobs

out.sim.2 <- out.sim.2[1:length(obs.2)]

out.2 <- data.frame('sim'=out.sim.2,'obs'=obs.2)


plot(out.2$sim,type='l',ylim=c(0,0.0005)) 
lines(out.2$x,type='l',col='red')

NSE(sim=out.2$sim,obs=out.2$x)
NSE(sim=log(out.2$sim+.0000000001),obs=log(out.2$x+.0000000001))
KGE(sim=out.2$sim,obs=out.2$x)
KGE(sim=log(out.2$sim+.0000000001),obs=log(out.2$x+.0000000001))

```
Okay good... the model works with the new spatial discretization. 

Now on to the hydromet inputs... 
